Efficient Handling of String-Number Conversion

### 2020-03-30 final-version/evaluation.tex
update to address the comments of Reviewer B (and the PASS question by Reviewer C)

We compare {\tool} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version. \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.

@@

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3-str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
								& UNSAT    & 16393& 15726& 16115& 15396 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &   142&  1480&   914&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     1&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
								& UNSAT    &   720&   667&   724&   644 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &    20&     6&    16&     4 \\ 
								& UNSAT    &     0&     0&     0&     0 \\
								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
								& UNSAT    & 17113& 16393& 16839& 16040 \\
								& UNKNOWN  &     0&     0&     0&   668 \\
								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
								& ERROR    &     0&     0&     0&   373 \\
								& INCORRECT&     1&     0&     0&   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

\begin{table}[h]
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3-str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3-str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
								& UNSAT    & 16393& 15726& 16115& 15396 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &   142&  1480&   914&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     1&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
								& UNSAT    &   720&   667&   724&   644 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{6}{*}{JavaScript}		& SAT      &    20&     3&    16&     4 \\ 
								& UNSAT    &     0&     0&     0&     0 \\
								& UNKNOWN  &     0&     9&     0&     0 \\
								& TIMEOUT  &     0&     8&     4&    10 \\
								& ERROR    &     0&     0&     0&     6 \\
								& INCORRECT&     0&     0&     0&     0 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
								& UNSAT    & 17113& 16393& 16839& 16040 \\
								& UNKNOWN  &     0&     0&     0&   668 \\
								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
								& ERROR    &     0&     0&     0&   373 \\
								& INCORRECT&     1&     0&     0&   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

@@

We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s. Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3Str3 got almost the same number of failed cases. Z3 also managed to reduce the number of failed cases to 821. %If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.

@@

\begin{table}[h]
\centering
\caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.9}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
2 			& \textbf{SAT}(0.27s)  &  \textbf{SAT}(0.89s) & \textbf{SAT}(0.45s) & \textbf{ERROR} \\
3  			& \textbf{SAT}(0.29s)  &  \textbf{SAT}(1.17s) & \textbf{SAT}(0.10s) & \textbf{ERROR} \\
4 			& \textbf{SAT}(0.37s)  &  \textbf{SAT}(4.92s) & \textbf{TIMEOUT}    & \textbf{ERROR} \\
5 			& \textbf{SAT}(0.39s)  &  \textbf{SAT}(11.27s)& \textbf{TIMEOUT}    & \textbf{ERROR} \\
6 			& \textbf{SAT}(0.41s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.13s) & \textbf{UNKNOWN} \\
7 			& \textbf{SAT}(0.51s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
8 			& \textbf{SAT}(0.53s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.29s) & \textbf{ERROR} \\
9 			& \textbf{SAT}(0.63s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
10 			& \textbf{SAT}(0.69s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.48s) & \textbf{TIMEOUT} \\
11 			& \textbf{SAT}(0.71s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.36s) & \textbf{ERROR} \\
12 			& \textbf{SAT}(0.74s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.38s) & \textbf{TIMEOUT} \\ \hline
\end{tabular}}
\label{table:checkLuhn}
\end{table}

@@

\hide{ % keep data of abc and ostrich
\begin{table}[h]
\centering
\caption{Results of Z3-Trau, CVC4, and Z3 on Basic String Constraint benchmarks (numbers with * will be updated later)}
\scalebox{0.7}{
\begin{tabular}{|l r | r r r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18490 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3855 &   3839*  & 3828 & 0 & 871 \\
							& $\times$ &  1977*   &  1824* &  3076 &  18558*  & 2444 & 25421 & 24439 \\ \hline
\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   316 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   206 &    190*  & 339 & 158 & 0 \\
							& $\times$ &   269*   &   148* &   543 &    382*  & 38 & 468 & 1065 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   807 &    772*  & 500 & 443 & 17 \\
							& $\times$ &     5*   &     6* &    16 &     55*  & 88 & 76 & 797 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1020 &    958*  & 596 & 349 & 22 \\
							& $\times$ &     2*   &   101* &    19 &     71*  & 137 & 120 & 978 \\ \hline
\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 2824 & 2205* & 2079 & 1972 & 2079 \\
							& $\times$ & 0* & 0* & 567 & 1186* & 84 & 383 & 13 \\ \hline \hline
\multirow{3}{*}{Total} 		& sat      & * & * & 19724 & * &  &  &  \\
							& unsat    & * & * & 10597 & * &  &  &  \\
							& $\times$ & * & * &  4702 & * &  &  &  \\\hline
\end{tabular}}
\label{table:base_benchmark}
\end{table}
}

\hide{ %3rd version of tables
\begin{table}[t]
	\centering
	\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
	\scalebox{0.7}{
		\begin{tabular}{l r | r r r r}
			\hline
			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
			\multirow{3}{*}{String-Number}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
			& unsat    &  17088*  & 16377* & 16832* &  16034* \\
			& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline

@@

\hide{  % 2nd version of tables
\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
							& timeout  &  1969*   &     0* &  3211 &  16708*  & 2444 & 0 & 44 \\
							& $\times$ &     8*   &  1824* &     0 &   1850*  & 0 & 25421 & 24395 \\ \hline
\multirow{4}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& timeout  &   185*   &   174* &   481 &     93*  & 386 & 308 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    358*  & 0 & 1 & 599 \\ \hline
\multirow{4}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& timeout  &    26*   &    21* &     0 &     83*  & 15 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    133*  & 46 & 2666 & 890 \\ \hline
\multirow{4}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
							& timeout  &   267*   &    63* &   549 &    377*  & 29 & 297 & 0 \\
							& $\times$ &     2*   &    85* &     0 &      5*  & 9 & 171 & 1065 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
							& timeout  &     5*   &     6* &    15 &     41*  & 23 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &     14*  & 65 & 76 & 797 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
							& timeout  &     2*   &    12* &    17 &     53*  & 50 & 0 & 0 \\
							& $\times$ &     0*   &    89* &     0 &     18*  & 87 & 120 & 978 \\ \hline
\multirow{4}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
							& timeout  & 0* & 0* & 631 & 1186* & 84 & 361 & 9 \\
							& $\times$ & 0* & 0* & 2760 & 0* & 0 & 22 & 4 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                           & {\tool} & CVC4   &    Z3  & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
									& unsat    &  17088*  & 16377* & 16034* &  16832* & 1609 & 0 & 213 \\
									& timeout  &   1191*  &  3011* &  4131* &   2010* & 439 & 0 & 144 \\
									& $\times$ &      0*  &     0* &   986* &      0* & 19367 & 21573 & 21169 \\ \hline
\multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* & 159 & 0 & 47 \\
									& unsat    &   2912*  &  2211* &  2655* &   1944* & 70 & 0 & 0 \\
									& timeout  &   1203*  &  2975* &  2012* &   4106* & 475 & 0 & 119 \\
									& $\times$ &     0*   &     0* &     0* &    922* & 6492 & 7396 & 7230 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}
}

>>>>

We compare {\tool} \changed{(\texttt{9831ad0cd})} with other state-of-the-art string solvers, namely, CVC4~(45bcf28ab)~\cite{cvc4Tool}, and Z3~(\texttt{d95b549ff})~\cite{z3}, \textsf{Z3Str3}~(\texttt{d95b549ff})~\cite{zheng2013z3}. For these tools, we use the GitHub version stated in the parenthesis because their performance are in general better than the corresponding release version. \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support all string functions in our benchmarks, especially string-number conversion.

@@

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{PyEx}		& SAT      & 19166& 19899& 16331&  3037 \\
							& UNSAT    &  3877&  3848&  3831&  3830 \\
							& UNKNOWN  &     0&     0&     0&     7 \\
							& TIMEOUT  &  2378&  1674&  5259& 16872 \\
							& ERROR    &     0&     0&     0&  1675 \\
							& INCORRECT&     1&     0&     0&    14 \\ \hline
\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
							& UNSAT    &   286&   214&   100&   111 \\
							& UNKNOWN  &     0&     0&     0&   345 \\
							& TIMEOUT  &   188&   335&   487&    89 \\
							& ERROR    &     0&     0&     0&    20 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{LeetCode}	& SAT      &   827&   865&   881&   661 \\
							& UNSAT    &  1784&  1785&  1785&  1780 \\
							& UNKNOWN  &     0&     0&     0&   122 \\
							& TIMEOUT  &    55&    16&     0&    90 \\
							& ERROR    &     0&     0&     0&    13 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{StringFuzz}	& SAT      &   478&   704&   267&   505 \\
							& UNSAT    &   283&   245&   188&   192 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &   304&   116&   610&   364 \\
							& ERROR    &     0&     0&     0&     0 \\
							& INCORRECT&     0&     0&     0&     0 \\\hline
\multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
							& UNSAT    &   818&   818&   808&   774 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &     4&     6&    15&    38 \\
							& ERROR    &     0&     0&     0&     9 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    11&     8&     5&    16 \\
							& UNSAT    &  1027&  1025&  1022&   957 \\
							& UNKNOWN  &     0&     0&     0&     3 \\
							& TIMEOUT  &     7&    12&    18&    58 \\
							& ERROR    &     0&     0&     0&     8 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
\multirow{6}{*}{Total} 		& SAT      & 20621& 21538& 17509&  4262 \\
							& UNSAT    &  8075&  7935&  7734&  7644 \\
							& UNKNOWN  &     0&     0&     0&   485 \\
							& TIMEOUT  &  2936&  2159&  6389& 17511 \\
							& ERROR    &     0&     0&     0&  1725 \\
							& INCORRECT&     1&     0&     0&    28 \\\hline
\end{tabular}}
\label{table:base_benchmark}}
\end{table}

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2392&  1721&  1898&   239 \\ 
								& UNSAT    & 16393& 15726& 16115& 15396 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &   142&  1480&   914&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     1&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &   670&   579&   914&   206 \\ 
								& UNSAT    &   720&   667&   724&   644 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &  1256&  1400&  1008&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{3}{*}{JavaScript}		& SAT      &    20&     6&    16&     4 \\ 
								& UNSAT    &     0&     0&     0&     0 \\
								& TIMEOUT  &     0&    14&     4&    16 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  3082&  2306&  2828&   449 \\ 
								& UNSAT    & 17113& 16393& 16839& 16040 \\
								& UNKNOWN  &     0&     0&     0&   668 \\
								& TIMEOUT  &  1398&  2894&  1926&  4063 \\
								& ERROR    &     0&     0&     0&   373 \\
								& INCORRECT&     1&     0&     0&   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
}
\end{table}

@@

%We also ran experiments on the String-Number Conversion benchmark with the timeout set to 30s. Provided more time for solving, {\tool} managed to obtain more results and the number of failed cases is reduced to 539, while CVC4 and Z3Str3 got almost the same number of failed cases. Z3 also managed to reduce the number of failed cases to 821. %If we exclude results on the Python core function that converts an IPv6 address to a number mentioned above, {\tool} has only $53$ timeouts in total while z3 has $809$ in total.

@@

\begin{table}[h]
\changed{

\centering
\caption{Comparison of {\tool}, CVC4, Z3, and Z3str3 with checkLuhn problems of 2 to 12 loops.}
\scalebox{0.8}{
\begin{tabular}{| c | c c c c|}
\hline
\# of Loops & {\tool} 			   &  CVC4    	 		  &       Z3   			& Z3Str3 \\ \hline
2 			& \textbf{SAT}(0.27s)  &  \textbf{SAT}(0.89s) & \textbf{SAT}(0.45s) & \textbf{ERROR} \\
3  			& \textbf{SAT}(0.29s)  &  \textbf{SAT}(1.17s) & \textbf{SAT}(0.10s) & \textbf{ERROR} \\
4 			& \textbf{SAT}(0.37s)  &  \textbf{SAT}(4.92s) & \textbf{TIMEOUT}    & \textbf{ERROR} \\
5 			& \textbf{SAT}(0.39s)  &  \textbf{SAT}(11.27s)& \textbf{TIMEOUT}    & \textbf{ERROR} \\
6 			& \textbf{SAT}(0.41s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.13s) & \textbf{UNKNOWN} \\
7 			& \textbf{SAT}(0.51s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
8 			& \textbf{SAT}(0.53s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.29s) & \textbf{ERROR} \\
9 			& \textbf{SAT}(0.63s)  &  \textbf{TIMEOUT}    & \textbf{TIMEOUT}    & \textbf{ERROR} \\
10 			& \textbf{SAT}(0.69s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.48s) & \textbf{TIMEOUT} \\
11 			& \textbf{SAT}(0.71s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.36s) & \textbf{ERROR} \\
12 			& \textbf{SAT}(0.74s)  &  \textbf{TIMEOUT}    & \textbf{SAT}(0.38s) & \textbf{TIMEOUT} \\ \hline
\end{tabular}}
\label{table:checkLuhn}}
\end{table}

@@

\hide{ % keep data of abc and ostrich
\begin{table}[h]
\centering
\caption{Results of Z3-Trau, CVC4, and Z3 on Basic String Constraint benchmarks (numbers with * will be updated later)}
\scalebox{0.7}{
\begin{tabular}{|l r | r r r r r r r|}
\hline
\multicolumn{2}{|c}{}                   & {\tool} & CVC4  &Z3 & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18490 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3855 &   3839*  & 3828 & 0 & 871 \\
							& $\times$ &  1977*   &  1824* &  3076 &  18558*  & 2444 & 25421 & 24439 \\ \hline
\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   316 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   206 &    190*  & 339 & 158 & 0 \\
							& $\times$ &   269*   &   148* &   543 &    382*  & 38 & 468 & 1065 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   807 &    772*  & 500 & 443 & 17 \\
							& $\times$ &     5*   &     6* &    16 &     55*  & 88 & 76 & 797 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1020 &    958*  & 596 & 349 & 22 \\
							& $\times$ &     2*   &   101* &    19 &     71*  & 137 & 120 & 978 \\ \hline
\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 2824 & 2205* & 2079 & 1972 & 2079 \\
							& $\times$ & 0* & 0* & 567 & 1186* & 84 & 383 & 13 \\ \hline \hline
\multirow{3}{*}{Total} 		& sat      & * & * & 19724 & * &  &  &  \\
							& unsat    & * & * & 10597 & * &  &  &  \\
							& $\times$ & * & * &  4702 & * &  &  &  \\\hline
\end{tabular}}
\label{table:base_benchmark}
\end{table}
}

\hide{ %3rd version of tables
\begin{table}[t]
	\centering
	\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
	\scalebox{0.7}{
		\begin{tabular}{l r | r r r r}
			\hline
			\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3Str3 \\ \hline
			\multirow{3}{*}{String-Number}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
			& unsat    &  17088*  & 16377* & 16832* &  16034* \\
			& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline

@@

\hide{  % 2nd version of tables
\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
							& timeout  &  1969*   &     0* &  3211 &  16708*  & 2444 & 0 & 44 \\
							& $\times$ &     8*   &  1824* &     0 &   1850*  & 0 & 25421 & 24395 \\ \hline
\multirow{4}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& timeout  &   185*   &   174* &   481 &     93*  & 386 & 308 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    358*  & 0 & 1 & 599 \\ \hline
\multirow{4}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& timeout  &    26*   &    21* &     0 &     83*  & 15 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    133*  & 46 & 2666 & 890 \\ \hline
\multirow{4}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
							& timeout  &   267*   &    63* &   549 &    377*  & 29 & 297 & 0 \\
							& $\times$ &     2*   &    85* &     0 &      5*  & 9 & 171 & 1065 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
							& timeout  &     5*   &     6* &    15 &     41*  & 23 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &     14*  & 65 & 76 & 797 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
							& timeout  &     2*   &    12* &    17 &     53*  & 50 & 0 & 0 \\
							& $\times$ &     0*   &    89* &     0 &     18*  & 87 & 120 & 978 \\ \hline
\multirow{4}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
							& timeout  & 0* & 0* & 631 & 1186* & 84 & 361 & 9 \\
							& $\times$ & 0* & 0* & 2760 & 0* & 0 & 22 & 4 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                           & {\tool} & CVC4   &    Z3  & Z3Str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
									& unsat    &  17088*  & 16377* & 16034* &  16832* & 1609 & 0 & 213 \\
									& timeout  &   1191*  &  3011* &  4131* &   2010* & 439 & 0 & 144 \\
									& $\times$ &      0*  &     0* &   986* &      0* & 19367 & 21573 & 21169 \\ \hline
\multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* & 159 & 0 & 47 \\
									& unsat    &   2912*  &  2211* &  2655* &   1944* & 70 & 0 & 0 \\
									& timeout  &   1203*  &  2975* &  2012* &   4106* & 475 & 0 & 119 \\
									& $\times$ &     0*   &     0* &     0* &    922* & 6492 & 7396 & 7230 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}
}
